Differential invariant signatures for planar Lie group transformations of images

### 2019-08-14 paper/newpaper.tex
With more, not necessarily better, words

\documentclass[review,onefignum,onetabnum]{siamonline171218}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}

\date{\today}
\title{Working title}
\author{Not-working authors}

@@

@@

Consider $\mathbf{x}_i \ in \mathbb{R}^2, i=1,2$, so that $mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$. Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.  Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$. Then the Omega Process is a second-order differential operator defined by:

@@

\centering
\begin{tabular}{cccc}
Degree & Weight & Diagram & Invariant \\
\hline
2 & 2 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $fxx$ \\

@@

@@

@@

\todo[inline]{Intro to model bit above. Steal equations from dispaper. TBC}
Cartan developed the moving frame to compute invariants.

@@

\todo[inline]{Largely discursive? Except conformal.}

>>>>

\documentclass[review,onefignum,onetabnum]{siamonline190516}
\usepackage{amsmath,amsfonts,graphicx}
\def\R{\mathbb{R}}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{tikz}

\date{\today}
\title{Differential invariant signatures for planar Lie group transformations of images}
\author{Not-working authors}

@@

The setting that we will consider is a transformation group $\mathcal{G}$ acting on a manifold $\mathcal{M}$ of dimension $n$. A $d$-th order differential invariant is a local scalar function $I: J^{d} (\mathbb{R}, \mathcal{M} ) \to \mathbb{R}$ that is invariant under the action of $\mathcal{G}$, i.e., $I(g(x,u^{(d)})) = I(x, u^{(d)}) \forall g \in \mathcal{G}$, where $J^{d}$ denotes the $d$-th order jet space.

====
Let $G$ be a (finite or infinite-dimensional) local planar transformation group. 
A {\em $k$-colour image} is a triple $(f,\Omega,k)$ where $\Omega\subset\R^2$, $1\le k\in\mathbb{Z}$,
and $f\colon\Omega\to\R^k$. The function $f$ will be taken to be as smooth as necessary.
A transformation $\varphi\in G$ acts on images by $\varphi\cdot (f,\Omega,k) = (f\circ\varphi^{-1},\varphi(\Omega),k)$.
(As we work locally, we will usually omit the domain $\Omega$; if the number of colours $k$ is not given, we assume $k=1$.)  A differential invariant is an invariant of the prolonged action of $G$ on the derivatives of $f$, i.e., a function $I$ of the values of $f$ and its derivatives at a point such that $I(f)(x,y) = I(\varphi\cdot f)(\varphi(x,y))$. An {\em $m$-dimensional signature set} is the image of $m$ invariants $\mathcal{I}=(I_1,I_2,\dots,I_m)$, i.e. the
set $\mathcal{I}(f)(\Omega)\subset \mathbb{R}^m$. 
A signature set is complete for $f$ if it determines $f$ up to transformations from $G$, i.e. if $\mathcal{I}(\tilde f)(\tilde\Omega) = \mathcal{I}(f)(\Omega)$ implies there exists a transformation $\varphi\in G$ such that $\tilde f = \varphi\cdot f$ and $\tilde \Omega = \varphi(\Omega)$.

An algorithm to compute invariants and determine complete signature sets is described in \cite{olver2001}. First, the
entire set of invariants is computed using the method of moving frames. Second, determine the differential invariant order $s$ of $f$. Then the signature set of a maximal set of functionally independent invariants of order $s+1$ is complete. A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.

While we follow this approach in general, in specific cases we have computed invariants using other techniques
including the invariant tensor theorem and classical invariant theory. We shall see that this yields insights into the relationships between the different groups. We develop our approach through examples of progressively more complicated groups.
===

local invariants -> occlusions OK
derivatives -> noise is not

signatures, dimensions, orders

Is this helpful? 
\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
\node(C1) [] {Diff};
\node(C2) [below left of=C1] {$\mathrm{Diff}_{\mathrm{vol}}$};
\node(C3) [below right of=C1] {$\mathrm{Diff}_{\mathrm{con}}$};
\node(A1) [below right of=C3]                          {$PSL(2,\mathbb{C})$};
\node(B1)    [below of=C2]    {$PSL(3,\mathbb{R})$};
\node(B2)   [below of=B1]              {$A(2)$};
\node(A2)       [below left of=A1]          {Sim$(2)$};
\node(A3)      [right of=A2]              {$PSL(2,\mathbb{R})$};
\node(B3)   [below of=B2]            {$SA(2)$};
\node(A4)      [below of=A2]            {$E(2)$};
\node(A5) [below right of=A4]{Translation};

\draw[thick,->] (C1) to  (C2);
\draw[thick,->] (C1) to  (C3);
%\draw[thick,->] (C1) to  (A2);
\draw[thick,->] (C3) to  (A1);
\draw[thick,->] (A1)   to (A2);
\draw[thick,->] (A1)    to (A3);
\draw[thick,->] (B1) to  (B2);
\draw[thick,->] (B2) to  (B3);
\draw[thick,->] (A2) to  (A4);
\draw[thick,->] (B3) to  (A4);
\draw[thick,->] (A3) to  (A5);
\draw[thick,->] (A4) to  (A5);
\end{tikzpicture}
\end{center}
\caption{The lattice of groups considered in this paper. The edges identify subgroups.}
\end{figure}

%Groups we've done:

%translations, E(2), Sim(2), SA(2), A(2), PSL(2,C), PSL(3,R), Diff\_con, Diff\_vol, Diff

SE(2) is done via the moving frame by Olver in Ch 8 of CIT.

@@

Consider $\mathbf{x}_i \in \mathbb{R}^2, i=1,2$, so that $\mathbf{x}_i$ can be written in coordinates as $(x_i, y_i)$. Then a pair of such $\mathbf{x}$ lie in $\mathbb{R}^2 \times \mathbb{R}^2$.  Now consider applying an affine transformation to each $\mathbf{x}$ independently: $\mathbf{x}_i \mapsto A \mathbf{x}_i + b$ where $A \in GL(2,\mathbb{R}$ and $b \in \mathbb{R}^2$. Then the Omega Process is a second-order differential operator defined by:

@@

\begin{tabular}{cccc}
\centering
Degree & Weight & Diagram & Invariant \\
\hline
2 & 2 &
\begin{tikzpicture}
    \node[draw,circle,minimum size=0.2cm] (1) at (-0.5,0) {1};
    \node[draw,circle,minimum size=0.2cm] (2) at (0.5,0) {2};
    \draw[-] (1) to [out=30,in=150] (2);
    \draw[-] (1) to [out=-30,in=-150] (2);
\end{tikzpicture}
& $fxx$ \\

@@

E2:
{\bf Aside 3. Role of the invariants} 
All of the 2nd order differential invariants play known roles in geometric analysis:
\begin{enumerate}
\item $f_if_i=\|\nabla f\|^2$ is the Lagrangian density for the Laplacian;
\item $f_{ii}$ is the Laplacian, which plays a key role in Euclidean and conformal geometry;
\item $f_{ij}f_i f_j$ is the `infinity-Laplacian'; critical points of $\|\nabla f\|_{L^\infty}$ obey the PDE $f_{ij}f_i f_j=0$;
\item
$f_{ij}f_i f_j$ is also a Lagrangian density for $-2\det f_{ij}$, which arises in Monge--Amp\`ere equations and
which can be written in terms of the final 2nd order invariant as $-2 \det f_{ij} = f_{ij}f_{ij}-f_{ii}^2$.
\end{enumerate}
In addition, we shall see in later sections that functions of these invariants are invariants or
relative invariants for many groups that contain $E(2)$, namely $Sim(2)$, $SA(2)$, $A(2)$, $PSL(3,\mathbb{R})$, $PSL(2,\mathbb{C})$, and the conformal group.

@@

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/SE2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/SE2Transform_signature.png}
\caption{A sample $SE(2)$ Transform and 3D signature.}
\label{fig:SE2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/E2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/E2Transform_signature.png}
\caption{A sample $E(2)$ Transform and 3D signature.}
\label{fig:E2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/SA2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/SA2Transform_signature.png}
\caption{A sample $SA(2)$ Transform and 3D signature.}
\label{fig:SA2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/A2Transform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/A2Transform_signature.png}
\caption{A sample $A(2)$ Transform and 3D signature.}
\label{fig:A2}
\end{figure}

@@

The method of moving frames enables one to identify invariants under the action of groups of transformations. It has a long history, as summarised in \cite{Olver14}; particularly noteworthy contributions are by Cartan~\cite{Cartan37} and Olver and co-authors; see~\cite{Olver14} for an overview, and note particularly for an application to~\cite{Calabi98}. The method is described in detail in~\cite{OlverCIT}r.

A right moving frame is a smooth $\mathcal{G}$-equivariant map $\rho : \mathcal{M} \to \mathcal{G}$ such that $\rho (g \cdot z) = \rho(z) \cdot g^{-1}$.

In order to construct differential invariants to the action of Lie group $\mathcal{G}$ acting on manifold $\mathcal{M}$, the procedure can be summarised as follows:

\begin{enumerate}
\item Prolong the group action to the jet space of $n$-th order derivatives (using implicit differentiation): $F: J^n \to \mathbb{R}$. 
\item Apply Cartan normalisation:
    \begin{enumerate}
    \item Choose a local cross-section to the group orbits, i.e., a ($n - \dim \mathcal{G}$)-dimensional submanifold $\mathcal{K}$ that intersects transversally at most once with each orbit
    \item $\mathcal{K}$ is specified by $\dim \mathcal{G}$ independent equations $Z_i (z) = c_i$, for $z \in J^n$,  and $Z_i$ scalar-valued functions and $c_i$ constants.
    \item The right moving frame $g = \rho(z)$ is found by solving the normalisation questions $Z_i (g \cdot z) = c_i$ for the group parameters $g$ (in terms of $z$).
    \end{enumerate}
\item The differential invariants are not affected by the action of the group: $I(g \cdot z) = I(z) \: \forall z \in \mathrm{dom} I$, or equivalently, if it is constant on the orbits. 
\item Hence $F$ is made invariant by transforming it with a group action: $I(z) = F(g \cdot z) |_{g=\rho(z)}$.  
\end{enumerate}

Olver uses the group $SE(2)$ as an example~\cite{Olver}, recovering the Euclidean curvature as a second-order invariant. We demonstrate the method with two groups: the M\"obius group ($PSL(2,\mathbb{C})$) and the projective group ($PSL(3,\mathbb{R})$).

\subsection{The M\"{o}bius Group}

The M\"obius group $\mathrm{PSL}(2,\mathbb{C})$ acts on the Riemann sphere
$\overline{\mathbb{C}} = \mathbb{C}\cup\infty$ by 
$$ \phi\colon \overline{\mathbb{C}} \to \overline{\mathbb{C}},\quad \phi(z) = \frac{\alpha z + \beta}{\gamma z + \delta},\quad \alpha,\beta,\gamma,\delta\in\mathbb{C}, \quad
\alpha\delta-\beta\gamma\ne 0.$$

Identifying $\R^2$ with $\mathbb{C}$, the M\"obius group is a real 6-dimensional local Lie group acting on $\mathbb{R}^2$.
It is the smallest nonlinear planar group that contains $SE(2)$, and it is the set of biholomorphic maps of the Riemann sphere; it also has direct applications in image processing since it arises in the {\em conformal camera} model of vision, in which scenes are projected radially onto a sphere \cite{lenz1990group,turski2004geometric}. 
%Different shapes may be related by M\"obius transformations, as is explored by Petukhov \cite{petukhov1989non} for biological objects: in one example, the human skull grows approximately by M\"obius transformations.  Note also that Thompson \cite{thompson1942growth} famously deformed images of one species to match those of another, many of his examples using conformal mappings, and thus may be approximated (or even determined by) M\"obius transformations. Discussing this work, Milnor \cite{milnor2010growth}  argued that ``The geometrically simplest way to change the relative size of different body parts would be by a conformal transformation. It seems plausible that this simplest solution will often be the most efficient, so that natural selection tend to choose it.'' (Milnor was thinking of 3D conformal transformations, whose restriction to 2D is the M\"obius transformations.)

The 0th order moving frame translates $z$ to $\beta$. We can therefore take $\beta=0$; we are also free to take $\delta=1$. This leaves 4 group parameters $a,b,c,d$, where $\alpha = a + i b$, $\gamma = c + i d$, to be determined as follows. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 5 invariants.

The prolonged action is:
\begin{equation}
\small
\arraycolsep=1.4pt
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & b & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -b & a & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 2\mu & -2 \rho & a^2 & 2 a b & b^2 & 0 & 0 & 0 & 0 \\
 2 \rho & 2\mu & -a b & a^2\!-b^2 & a b & 0 & 0 & 0 & 0 \\
 -2\mu & 2 \rho & b^2 & -2 a b & a^2 & 0 & 0 & 0 & 0 \\
 -6 (2 b c d+a \lambda) & 6 (2 a c d-b\lambda) & 6 a \mu &
  M_{64}  & -6 b \rho & a^3 & 3 a^2 b & 3 a b^2 & b^3 \\
 -6 (2 a c d-b\lambda) & -6 (2 b c d+a \lambda) & M_{73}& M_{74} & 
 M_{75} & -a^2 b & a^3\!-2 a b^2 & 2
   a^2 b\!-b^3 & a b^2 \\
 6 (2 b c d+a \lambda) & -6 (2 a c d-b\lambda) & M_{83} & M_{84} & M_{85} & a b^2 & b^3\!-2
   a^2 b & a^3\!-2 a b^2 & a^2 b \\
 6 (2 a c d-b\lambda) & 6 (2 b c d+a \lambda) & 6 b \mu & 
  M_{94} & 6 a \rho & -b^3 & 3 a b^2 & -3 a^2 b & a^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
\label{eqn:mobius}
 \end{equation}
 where
 \begin{equation*}
 \small
 \begin{array}{lll}
M_{64}=-12abc+6d(a^2-b^2), & 
M_{73}=4 d a^2+6 b c a-2 b^2 d, & 
M_{74}=-6 c a^2+12 b d a+6 b^2 c, \\
 M_{75}=-2 d a^2-6 b c a+4 b^2 d, &
 M_{83}=2 c a^2-6 b d a-4 b^2 c, &
 M_{84}=6 (d a^2+2 b c a-b^2 d),\\
 M_{85}=-4 c a^2+6 b d a+2 b^2 c,& 
 M_{94}= -12a b d + 6c(a^2-b^2),\\
\lambda=d^2-c^2, & 
\mu = b d - a c, & 
\rho = b c + a d.
\end{array}
\end{equation*}

The moving frame calculation now proceeds as follows.
\begin{enumerate}
\item The frame $\bar f_x=1$, $\bar f_y=0$ determines the group parameters
$$ a = f_x/(f_i f_i),\quad b = f_y/(f_i f_i).$$

\item The frame $\bar f_{xyy}=\bar f_{yy}=0$ determines the group parameters
$$ c = (2 f_xf_yf_{xyy} - f_{xx}f_y^2 - f_{yy}f_x^2)/(2 f_i f_i)^2$$
$$ d = (f_{xyy}f_x^2 - f_x f_y f_{xx} - f_{xyy}f_y^2 - f_{yy} f_x f_y)/(2 f_i f_i)^2.$$

\item The 2nd order invariant is then given by $\bar f_{xx}$ using Equation~(\ref{eqn:mobius}); it is 
$$\bar f_{xx} = \frac{f_{ii}}{f_i f_i}.$$

\item The four 3rd order invariants are then given by $\bar f_{xxx},\dots, \barf_{yyy}$ using Equation~(\ref{eqn:mobius}). They are
rational functions with numerators of degree 6 and denominators $(f_i f_i)^4$, and are relative invariants of weight 8.
\end{enumerate}

%It is clear that there must be 2 syzygies between the relative invariants $J_1,\dots,J_4,K_1,\dots,K_4$.
%They are easily found algebraically to be
%$$K_2 = -K_4 + J_1 J_4$$
%and
%$$K_3=-K_1 +J_1 J_3 + 2 J_1^2 J_2^2.$$

We want to work with polynomials, and so clear denominators. We choose to use $M_1 = f^4_{ii}$ and two of the four 3rd order invariants to form a M\"obius signature $(M_1, M_2, M_3)$, where: 
$M_2=
f_y ^5 f_{yyy} + \frac{9}{2} f_y ^2 f_{yy}^2 f_x ^2 + 
 f_y ^3 f_{yyy} f_x ^2 + \frac{3}{2} f_{yy}^2 f_x ^4 - 
 9 f_y ^3 f_{yy} f_x  f_{xy} + 
 3 f_y  f_{yy} f_x ^3 f_{xy} + \frac{3}{2} f_y ^4 f_{xy}^2 - 
 9 f_y ^2 f_x ^2 f_{xy}^2 + \frac{3}{2} f_z ^4 f_{xy}^2 + 
 3 f_y ^4 f_x  f_{xyy} + 3 f_y ^2 f_x ^3 f_{xyy} + 
 3 f_y ^4 f_{yy} f_{xx} + 3 f_{yy} f_x ^4 f_{xx} + 
 3 f_y ^3 f_x  f_{xy} f_{xx} - 
 9 f_y  f_x ^3 f_{xy} f_{xx} + \frac{3}{2} f_y ^4 f_{xx}^2 + 
 \frac{9}{2} f_y ^2 f_x ^2 f_{xx}^2 + 3 f_y ^3 f_x ^2 f_{xxy} + 
 3 f_y  f_x ^4 f_{xxy} + f_y ^2 f_x ^3 f_{xxx} + 
 f_x ^5 f_{xxx}, 
 $

 $M_3=-3 f_y  f_{yy}^2 f_x ^3 + 
 f_y ^2 f_{yyy} f_x ^3 + f_{yyy} f_x ^5 + 
 9 f_y ^2 f_{yy} f_x ^2 f_{xy} - 
 3 f_{yy} f_x ^4 f_{xy} - 6 f_y ^3 f_x  f_{xy}^2 + 
 6 f_y  f_x ^3 f_{xy}^2 - 3 f_y ^3 f_x ^2 f_{xyy} - 
 3 f_y  f_x ^4 f_{xyy} - 3 f_y ^3 f_{yy} f_x  f_{xx} + 
 3 f_y  f_{yy} f_x ^3 f_{xx} + 3 f_y ^4 f_{xy} f_{xx} - 
 9 f_y ^2 f_x ^2 f_{xy} f_{xx} + 
 3 f_y ^3 f_x  f_{xx}^2 + 3 f_y ^4 f_x  f_{xxy} + 
 3 f_y ^2 f_x ^3 f_{xxy} - f_y ^5 f_{xxx} - 
 f_y ^3 f_x ^2 f_{xxx}
$

The image $f$ and these 3 relative invariants of weight 8 provide a 3-dimensional signature; an example is shown in Figure~\ref{fig:mobius}, although note that it is singular when $f_x=f_y=f_{ii}=0$, a codimension 1 phenomenon for images.

%In previous work \cite{mobius}, two independent 3rd order M\"obius invariants were calculated
%from the classical M\"obius geometry of curves. Namely, the M\"obius arclength 
%of a curve is $\sqrt{|\kappa_s|}ds$, were $ds$ is Euclidean arclength. Under any conformal map $\phi$,
%both $ds$ and $1/\|\nabla f\|$ scale by $|\phi'|$. The sign of $\kappa_s$ is also  invariant,
%hence $\kappa_s/\|\nabla f\|^2$ is  invariant for any invariant curve. Calculating this invariant
%for the level sets of $f$ and for their orthogonal curves yields two invariants of $f$ that
%we call $\lambda_t$ and $\lambda_n$, respectively. Writing 
%them out in full and comparing to the invariants founds above shows that they are related very simply, by

%$$ \frac{K_2}{\|\nabla f\|^8} = \lambda_t$$
%$$\frac{K_4}{\|\nabla f\|^8} =\lambda_n$$

%We do not know of any equivalent characterization of the invariants $K_1$, $K_3$ in
%terms of classical M\"obius geometry.

%We now have that
%$$ (J_1^4, J_2^4, J_1 J_3, J_1 J_4, K_1, K_4)$$
%are 6 relative invariants of weight 8. Projecting any subset to a sphere provides a M\"obius signature.
%For example, the image $f$ together with the projection of $(J_1^4, J_2^4, K_1)$ provides a 3-dimensional signature.
%Any such signature that includes $J_1$ and $J_2$ is

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/MobiusTransform_signature.png}
\caption{A sample M\"obius Transform and 3D signature.}
\label{fig:mobius}
\end{figure}

\subsection{The Projective Group}

We consider the 8-dimensional group $\mathrm{PSL}(3,\R)$ acting on $\R^2$ by projective transformations, i.e., $$(x,y) \mapsto \left(\frac{a x + b y + j}{l + g x + h y}, \frac{c x + d y + k}{l+ g x + h y}\right).$$

The 0th order moving frame translates $(x,y)$ to $(0,0)$. We can therefore take $j=k=0$; we will also take $l=1$. This leaves 6 group parameters $(a,b,c,d,g,h)$ to be determined. First we prolong the action to 3rd derivatives of $f$. There are 9 derivatives of $f$ of order 1, 2, and 3, so there must be at least 3 invariants.

The prolonged action is:
\begin{equation}
\tiny
\arraycolsep=1.4pt
\label{eq:prolong}
\left(
\begin{array}{c}
  \bar f_x \\ \bar f_y \\ \bar f_{xx} \\ \bar f_{xy} \\ \bar f_{yy} \\ \bar f_{xxx} \\ \bar f_{xxy} \\ \bar f_{xyy} \\ \bar f_{yyy} 
 \end{array}
 \right)
 = 
\left(
\begin{array}{ccccccccc}
 a & c & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 b & d & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
 -2 a g & -2 c g & a^2 & 2 a c & c^2 & 0 & 0 & 0 & 0 \\
 -b g-a h & -d g-c h & a b & b c+a d & c d & 0 & 0 & 0 & 0 \\
 -2 b h & -2 d h & b^2 & 2 b d & d^2 & 0 & 0 & 0 & 0 \\
 6 a g^2 & 6 c g^2 & -6 a^2 g & -12 a c g & -6 c^2 g & a^3 & 3 a^2 c & 3 a c^2 & c^3 \\
 2 g (b g+2 a h) & 2 g (d g+2 c h) & -2 a (2 b g+a h) & -4 (b c g+a d g+a c h) & -2 c (2 d
   g+c h) & a^2 b & a (2 b c+a d) & c (b c+2 a d) & c^2 d \\
 2 h (2 b g+a h) & 2 h (2 d g+c h) & -2 b (b g+2 a h) & -4 (b d g+b c h+a d h) & -2 d (d g+2
   c h) & a b^2 & b (b c+2 a d) & d (2 b c+a d) & c d^2 \\
 6 b h^2 & 6 d h^2 & -6 b^2 h & -12 b d h & -6 d^2 h & b^3 & 3 b^2 d & 3 b d^2 & d^3 \\
\end{array}
\right)\left(
\begin{array}{c}
f_x \\ f_y \\ f_{xx} \\ f_{xy} \\ f_{yy} \\ f_{xxx} \\ f_{xxy} \\ f_{xyy} \\ f_{yyy} 
 \end{array}
 \right).
 \end{equation}

First, recall from the analysis of the subgroup $A(2)$ that under $f\mapsto f\circ \phi$, $\phi\in A(2)$, we have 
\begin{equation}
\label{eq:D}
D \mapsto (\det \phi')^2 D\circ \phi
\end{equation}
where $D = f_{x}^2 f_{yy} + f_y^2 f_{xx} - 2 f_x f_y f_{xyy}$.

A direct calculation using (\ref{eq:prolong}) shows that the same transformation rule (\ref{eq:D}) holds for $\phi\in\mathrm{PSL}(3,\R)$.  That is, $D$ is a relative invariant of weight 2 of this action. From (\ref{eq:D}), the sign of $D$ is invariant and therefore the choice of moving frame must depend on the sign of $D$.

\begin{enumerate}
\item The frame $\bar f_x = 1$  determines the group parameter $$a = (1-c f_y)/f_x.$$
\item The frame $\bar f_y=  0$ determines the group parameter $$b = -d f_y/f_x.$$
\item Substituting this choice of $a$ and $b$ and examining the dependencies of $f_{xx}$, $f_{xy}$, $f_{yy}$, and $f_{yyy}$ on the remaining group parameters allows them to be solved sequentially, as follows.
\item We have $\bar f_{yy} = d^2 D/f_x^2$; therefore if $D>0$ we choose the frame
$\bar f_{yy} = 1$ and $$d = f_x/D^{1/2}.$$
\item The frame $\bar f_{yyy} = 0$ determines the group parameter
$$ h = \frac{d(f_{yyy}f_x^3 - 3 f_x^2 f_y f_{xyy} + 3 f_x f_y^2 f_{xxy} - f_y^3 f_{xxx})}{6 f_x D}.$$
\item The frame $\bar f_{xyy}=0$ determines the group parameter
$$ c = \frac{h f_x^2}{d D} - \frac{f_x f_{xy} - f_y f_{xx}}{D}.$$
\item The frame $\bar f_{xx}=0$ determines the group parameter
$$ g = \frac{1}{2 f_x^2}(f_{xx} + 2 c ( f_x f_{xy} - f_y f_{xx} ) + c^2 D).$$
\end{enumerate}

\todo[inline]{Need to get the Js from somewhere...}
Having determined the frame, any function of the remaining derivatives $\bar f_{xxx}$, $\bar f_{xxy}$, and $\bar f_{yyy}$, as given in Equation~(\ref{eq:prolong}), provides invariants. We choose $$ (f_{xxx}, f_{xxy}^2, f_{xyy})=\left(\frac{J_1}{D^6},\frac{J_2}{D^9},\frac{J_3}{D^3}\right)$$
because these all have denominators given by integer powers  of $D$, resolving the issue caused
by the sign of $D$. Therefore,
$$ (D^{18}, J_1^3, J_2^2, J_3^6)$$
are all relative invariants of weight 36; so projecting any subset of them of them to a sphere
yields a 3rd order invariant signature.

However, these signatures can be simplified and made more robust, as follows.

The components of $J$ are polynomials of degree 16, 24, and 8, respectively, and are extremely complicated when written out explicitly. More seriously, $J$ vanishes on generic images. This can be seen as follows. 
Recall the $SA(2)$ invariant $E$ defined in (\ref{eq:E}).
%Let
%$$ E := f_{222}f_1^3 - 3 f_{122}f_1 f_2^2 + 3 f_{112}f_1^2 f_2 - f_{111}f_2^3$$
Then the components of $J$ have the structure
$$ J_1 = E^4 + D P_{13},\quad J_2 = (E^3 + D P_9)^2,\quad J_3=E^2 -12 D P_5$$
where the $P_n$ are polynomials of degree $n$. Therefore $J=0$ when $D=E=0$, which 
is a codimension 0 phenomenon for images. In particular, $D=E=0$ at critical points.

The structure of () suggests considering the combination $J_1 - J_3^2$ which turns out to obey
$$J_1 - J_3^2 = 144 D^4 P_4.$$
Therefore, as $J_1/D^6$ and $J_3/D^3$ are invariant, so is $P_4/D^2$. 
Moreover, {\em the numerator of this new invariant does not vanish at critical points.} 
It has the structure
$$P_4 = -4(\det f_{ij})^2 + Q_4,$$
where $Q_4$ is a polynomial of degree 4 that vanishes when $f_x=f_y=0$. In conclusion, the
relative invariant of weight 12
$$ (D^6, P_4^3, (E^2-12D P_5)^2)$$
can be projected to $S^2$ yielding a projective invariant of images that
is singular only when $D=E=P_4=0$, which is a codimension 1 phenomenon for images.
(One can check that $D=E=0\Rightarrow P_4=0$.) In particular, at critical points it tends to
$$ (0, (2\det f_{ij})^6, 0)$$
and hence critical points with $\det f_{ij}\ne 0$ have signature $(0,1,0)$.

For completeness we write out the invariants explicitly:

$Q_4=4 f_x  f_{xy} ^2 f_{xyy}  - 
f_x ^2 f_{xyy} ^2 - 
 2 f_{yyy}  f_x  f_{xy}  f_{xx}  + 
 2 f_{yy}  f_x  f_{xyy}  f_{xx}  - 
 6 f_{y}  f_{xy}  f_{xyy}  f_{xx}  + 
 2 f_{y}  f_{yyy}  f_{xx} ^2 + 
 f_{yyy}  f_x ^2 f_{xxy}  - 
 6 f_{yy}  f_x  f_{xy}  f_{xxy}  + 
 4 f_{y}  f_{xy} ^2 f_{xxy}  + 
 f_{y}  f_x  f_{xyy}  f_{xxy}  + 
 2 f_{y}  f_{yy}  f_{xx}  f_{xxy}  - 
 f_{y} ^2 f_{xxy} ^2 + 
 2 f_{yy} ^2 f_x  f_{xxx}  - 
 f_{y}  f_{yyy}  f_x  f_{xxx}  - 
 2 f_{y}  f_{yy}  f_{xy}  f_{xxx}  + f_{y} ^2 f_{xyy}  f_{xxx} $

$P_5=f_{yyy}  f_{x} ^3 f_{xy}  - 
f_{yy}  f_{x} ^2 f_{xy} ^2 + 
 2 f_{y}  f_{x}  f_{xy} ^3 - 
 f_{yy}  f_{x} ^3 f_{xyy}  - 
 f_{y}  f_{x} ^2 f_{xy}  f_{xyy}  + 
 f_{yy} ^2 f_{x} ^2 f_{xx}  - 
 f_{y}  f_{yyy}  f_{x} ^2 f_{xx}  - 
 2 f_{y}  f_{yy}  f_{x}  f_{xy}  f_{xx}  - 
 f_{y} ^2 f_{xy} ^2 f_{xx}  + 
 2 f_{y} ^2 f_{x}  f_{xyy}  f_{xx}  + 
 f_{y} ^2 f_{yy}  f_{xx} ^2 + 
 2 f_{y}  f_{yy}  f_{x} ^2 f_{xxy}  - 
 f_{y} ^2 f_{x}  f_{xy}  f_{xxy}  - 
 f_{y} ^3 f_{xx}  f_{xxy}  - 
 f_{y} ^2 f_{yy}  f_{x}  f_{xxx}  + 
 f_{y} ^3 f_{xy}  f_{xxx} $

Including $J_2$ in addition provides a 4-dimensional signature set, but does not increase the codimension of the set of bad images.

Further invariants can be found by noting that, for any planar transformation group and any two invariants
$I^1$ and $I^2$, $\nabla I^1 \times \nabla I^2$ is a relative invariant of weight 1; that is,
$$\nabla I^1 \times \nabla I^2\mapsto (\det \phi')(\nabla I^1 \times \nabla I^2).$$
Applying this operation to $f$ and the 4 3rd order invariants yields $5\cdot4/2=1$0  4th order invariants.

\begin{figure}
\centering
\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_transform.png}
\includegraphics[width=.45\textwidth]{Figs/PSL3RTransform_signature.png}
\caption{A sample $PSL(3,\mathbb{R})$ Transform and 3D signature.}
\label{fig:PSL3R}
\end{figure}

@@

Define diffeo here

\subsection{Conformal Diffeomorphisms $\mathbf{Diff}_{\mathbf{con}}$}

The group of conformal diffeomorphisms is the subgroup of diffeomorphisms that are angle-preserving, i.e.,

\begin{equation}
\angle (u,v) = \angle (D \phi(x) . u, D \phi(x).v)
\end{equation}

\noindent where $\angle(u, v)$ denotes the angle between tangent vectors $u$ and $v$ based at $x \in \mathbb{R}^2$, $\phi \in \Diff$ and $D$ represents the Jacobian. The group is infinite-dimensional, but still small enough that images have local differential invariants.

The M\"obius action is locally identical to the full conformal group up to and including second order. Therefore, there are no new conformal invariants, apart from the M\"obius ones, up to second order. Rather than applying the method of moving frames (which has been extended to Lie pseduo-groups in~\cite{}), we perform a direct calculation using the defining geometric properties of the conformal group.

At second order, we first consider the action of conformal maps on the Euclidean invariants $f_i f_i$ and $f_{ii}$.

Let $\psi := \varphi^{-1}$. For any diffeomorphism, the derivatives of $f$ transform as
$$f_i \mapsto f_j \psi^j_i$$
and
$$f_{ij} \mapsto f_{kl} \psi^k_i\psi^l_j + f_{k}\psi^k_{ij}.$$
Therefore the Laplacian of $f$ transforms as
$$ f_{ii} \mapsto f_{kl} \psi^k_i \psi^l_i + f_k \psi^k_{ii}.$$
When $\psi=u + i v$ is conformal, $\psi_{k,ii}=0$ because the components of conformal maps are harmonic functions,
and the Cauchy-Riemann equations give $\psi_{k,i}\psi_{l,i} = (u_x^2 + u_y^2)\delta_{kl}$. Therefore,
$$ f_{ii} \mapsto f_{ii}(u_x^2+u_y^2).$$
Here $u_x^2+u_y^2=\det\psi^k_i$ is the local scaling factor of the transformation.
Note also that
$$f_i f_i \mapsto f_k f_l \psi_{k,i} \psi_{l,i} = f_k f_k (u_x^2 + u_y^2).$$
That is, $f_{ii}$ and $f_i f_i$ are both relative invariants of weight 2, while $f_{ii}/(f_i f_i)$ is a conformal invariant, as we saw for the M\"obius group. By itself, it is not useful for images as it is singular at critical points of $f$.
